### 2020-08-23 spanish/sections/teaching.tex
Create teaching.tex
Update teaching.tex

\cvsection{Relevant Teaching Experience}

@@

\begin{itemize}
\item{\small Department of Politics and International Relations, {\bfseries University of Oxford}, Oxford, UK}
\begin{itemize}
\item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
\end{itemize}
\item{\small Faculty of Economics and Management, {\bfseries Universidad de Santiago}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Political Science I (undergraduate lecture), Spring 2014, 2018, Fall 2015-2019}
\item[$\circ$]{\small Political Science II (undergraduate lecture), Spring 2015-2018}
\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), Fall 2018}
\item[$\circ$]{\small Workshop for Research Design (graduate seminar), Spring 2017-2018}
\item[$\circ$]{\small Research Methodology (undergraduate lecture), Spring 2014-2015, Fall 2015-2017}
\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), Fall 2017}
\end{itemize}
\item{\small School of Government and Public Management, {\bfseries Universidad de Chile}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), Fall 2016}
\item[$\circ$]{\small Political Analysis (undergraduate lecture), Fall 2014}
\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), Spring 2013-2014}
\end{itemize}
\end{itemize}

>>>>

\cvsection{Experiencia en docencia relevante}

@@

\begin{itemize}
\item{\small Departamento de Política y Relaciones Internacionales, {\bfseries Universidad de Oxford}, Oxford, RU}
\begin{itemize}
\item[$\circ$]{\small Gobierno Comparado (tutorial de pregrado, Prof. Petra Schleiter), Hilary 2020}
\end{itemize}
\item{\small Facultad de Administración y Economía, {\bfseries Universidad de Santiago}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Ciencia Política I (curso de pregrado), primavera 2014, 2018, otoño 2015-2019}
\item[$\circ$]{\small Ciencia Política II (curso de pregrado), primavera 2015-2018}
\item[$\circ$]{\small Econometría para las Políticas Públicas (curso de pregrado), otoño 2018}
\item[$\circ$]{\small Taller de Diseño de Investigación (seminario de postgrado), primavera 2017-2018}
\item[$\circ$]{\small Metodología de la Investigación (curso de pregrado), primavera 2014-2015, otoño 2015-2017}
\item[$\circ$]{\small Introducción a los Métodos Cuantitativos (curso de pregrado), otoño 2017}
\end{itemize}
\item{\small Escuela de Gobierno y Gestión Pública, {\bfseries Universidad de Chile}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Estudio de los Fenómenos Políticos (curso de pregrado), otoño 2016}
\item[$\circ$]{\small Análisis Político (curso de pregrado), otoño 2014}
\item[$\circ$]{\small Elitismo y Democracia (curso de pregrado, Prof. Alejandro Olivares), primavera 2013-2014}
\end{itemize}
\end{itemize}
